Software Citation Principles

### 2016-03-24 sc-principles/software-citation-principles.tex
Fleshing out the NIH section

Life sciences/NIH: Software Discovery Index Meeting Report~\cite{software-discovery-index} a cross-disciplinary meeting
but with a largely biomedical-focus. Suggested minimal information about software (MIAS) standard. Discusses how a common set of metadata
fields are critical for useful indexing - suggested candidates for this list.

@@

\textbf{Existing efforts around metadata standards}

@@

Kyle Niemeyer, Oregon State University

>>>>

The Life sciences: In May 2014, the NIH held a workshop aimed at helping the biomedical community discover, cite and reuse software written by their peers. The primary outcome of this workshop was the Software Discovery Index Meeting Report~\cite{software-discovery-index}. The authors of the report cite discuss what framework would be required for supporting a Software Discovery Index including the need for unique identifiers, how citations to these would be handled by publishers and the critical need for metadata to describe software packages.

@@

\subsection{Existing efforts around metadata standards}

@@

Kyle E.~Niemeyer, Oregon State University
